\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\input{glyphtounicode}


% ----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 


\begin{document}

\begin{center}
  \textbf{\Huge \scshape Ahmad Sultan} \\ \vspace{1pt}
  \textbf{\small \scshape Software Engineer and Tech Trainer} \\ \vspace{5pt}
  \small +92 302 051 1167 $|$
  \href{mailto:ahmadjajja86@gmail.com}{ahmadjajja86@gmail.com}  $|$
  \href{https://www.linkedin.com/in/ahmad-jajja/}{\underline{LinkedIn}} $|$
  \href{https://github.com/Ahmadjajja}{\underline{GitHub}} $|$
  \href{https://ahmad-jajja.com/}{\underline{Website}} $|$
  \href{https://leetcode.com/ahmadjajja86/}{\underline{LeetCode}}
\end{center}

%-----------1 - ACHIEVEMENTS-----------
\section{\textbf{Achievements}}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape @Harvard University(CS50x\_PuzzleDay\_Winner):} Our team {\href{https://www.linkedin.com/feed/update/urn:li:activity:7184212040717131778/}{\underline{won 1st place}}} at CS50x Puzzle Day 2024 by solving 9/9 complex puzzles.}
\resumeItem{\textcolor{blue}{\itshape Duolingo English Test:} Successfully {\href{https://www.linkedin.com/feed/update/urn:li:activity:7205506772109783041/}{\underline{Obtained}} 125/160 Score(Which is equivalent to IELTS 6.5 or higher bands).}}
\resumeItem{\textcolor{blue}{\itshape @GitHub:} {\href{https://committers.top/pakistan\#Ahmadjajja}{\underline{Top 16th Pakistani GitHub contributor}}} with 700+ days of coding consistency and numerous achievements.}
\resumeItem{\textcolor{blue}{\itshape @Stanford University(Code\_in\_Place):} {\href{https://www.linkedin.com/feed/update/urn:li:activity:7186385467846639620/}{\underline{Selected}}} as a Section Leader to teach Python to 100+ international students.}
\resumeItem{\textcolor{blue}{\itshape @{\href{https://saylaniwelfareusa.com/en/services/education/technical-education/saylani-mass-it-training}{\underline{SMIT:}}}}  {\href{https://www.linkedin.com/posts/ahmad-jajja_learn-to-code-with-activity-7151895134744256512-Dmyf?utm_source=share&utm_medium=member_desktop}{\underline{Trained}}} 2,000+ students in different programming languages and technologies.}
% \resumeItem{\textcolor{blue}{\itshape @{\href{https://www.linkedin.com/company/icode-guru/mycompany/}{\underline{iCodeGuru:}}}} Volunteering to teach and mentor underprivileged students {\href{https://github.com/Ahmadjajja/LeetCode_Volunteer_Teaching}{\underline{Python, DSA (LeetCode)}}}, and {\href{https://www.linkedin.com/feed/update/urn:li:activity:7169346246216671232/}{\underline{Duolingo}}} English Proficiency.{\href{https://github.com/Ahmadjajja/LeetCode_Volunteer_Teaching}{\underline{[Videos Playlist]}}}}
\resumeItem{\textcolor{blue}{\itshape @leetcode:} {\href{https://leetcode.com/ahmadjajja86/}{\underline{Solved}}} 300+ Data Structures and Algorithms problems.[{\href{https://github.com/Ahmadjajja/JAVA_DSA}{\underline{Github link}}}]}
\resumeItem{\textcolor{blue}{\itshape @lablab.ai:} {\href{https://lablab.ai/u/@ahmad_jajja288}{\underline{Participated}}} in multiple AI International Hackathons and \href{https://www.linkedin.com/feed/update/urn:li:activity:7176624410651504641/}{\underline{won}} one of them (Unhallucinate Challenge).}
% \resumeItem{\textcolor{blue}{\itshape @lablab.ai:} { of an International Hackathon(Unhallucinate Challange).}}
% \resumeItem{{\href{https://github.com/Ahmadjajja/Social_Real_Estate_System_Mobile_App_Frontend}{\underline{Participated}}} in a national hackathon @SMIT, developed the “Social Real Estate System” mobile app.}
\resumeItem{\textcolor{blue}{\itshape {\href{https://www.linkedin.com/posts/ahmad-jajja_guestabrspeaker-activity-7215704636224135168-LNH3?utm_source=share&utm_medium=member_desktop}{\underline{Guest Speaker at WordSprint Hackathon 3.0}}}:} Gave a talk on "Bridging the Gap: From Coding Basics to Real-World Solutions". }
\resumeItem{\textcolor{blue}{\itshape Fully-funded scholarship:} Recipient of merit-based fully-funded scholarship in bachelors.}
% \resumeItem{\textcolor{blue}{\itshape Working experience:} 3+ years as a Software Engineer.}

\resumeItemListEnd

%-----------2 - Technical SKILLS-----------
\section{\textbf{Technical Skills}}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape \textcolor{blue}{\itshape Programming Languages:}}{ C, C++, Dart, Java, Python, JavaScript (ES6+), TypeScript } \\}
\resumeItem{\textcolor{blue}{\itshape Web Dev:}{ HTML5, CSS3, SCSS, SASS, Bootstrap 5, Chakra UI, Ant Design, React JS(Context API, Router, State Management)} \\}
\resumeItem{\textcolor{blue}{\itshape Mobile Dev:}{ React Native} \\}
\resumeItem{\textcolor{blue}{\itshape Backend:}{ Firebase, Node JS, Express JS, Python, Flask, Django} \\}
\resumeItem{\textcolor{blue}{\itshape AI:}{ Generative AI, LLMs, RAG (Vectara)} \\}
\resumeItem{\textcolor{blue}{\itshape Version Control:}{ Git, Github} \\}
\resumeItem{\textcolor{blue}{\itshape APIs:}{ Rest-APIs, GraphQL} \\}
\resumeItem{\textcolor{blue}{\itshape Databases:}{ MongoDB, Firestore}\\}
\resumeItemListEnd
%

%-----------3 - EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeSubheading
{The University of Agriculture, Faisalabad}{Sep 2020 - Jun 2024}
{}{}
{CGPA: 3.35 / 4.00}{}
\resumeItemListStart
\resumeItem{Bachelor of Science in Computer Science}
% \resumeItem{Coursework: Data Structures and Algorithms, Object Oriented programming (OOPs), DBMS, Operating System}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------4 - Final Year project-----------
\section{\textbf{Final Year Project}}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{{AI Podcast Generator}} $|$ \emph{HTML, CSS, Bootstrap5, Javascript, React, firebase, Generative AI, LLMs, python} $|$ [{\href{https://github.com/Ahmadjajja/AIpodcastgenerator}{\underline{Github link}}}]} {}
\resumeItemListStart
\resumeItem{Created an AI platform to turn text articles and youtube videos into audio podcasts.}
\resumeItem{Used Python, OpenAI, and ElevenLabs for content and voice synthesis.}
\resumeItem{Designed a user-friendly interface with secure Firebase authentication \& Enabled customizable voice options.}
\resumeItemListEnd
\resumeSubHeadingListEnd



%-----------5 - Work EXPERIENCE-----------
\section{\textbf{Work Experience}}
\resumeSubHeadingListStart

\resumeSubheading
{Co-Founder \& Dev Lead}{Feb 2024 -- Present}
{{\href{https://www.linkedin.com/company/ecofactorai/}{\underline{EcoFactor}}}}{São Paulo, Brazil · Remote}
\resumeItemListStart
\resumeItem{EcoFactor uses AI to boost manufacturing sustainability and efficiency, guiding eco-friendly practices and optimizing workflows.[{\href{https://www.linkedin.com/feed/update/urn:li:activity:7172699152647110656/}{\underline{See Software}}}]}
\resumeItem{{\href{https://www.linkedin.com/posts/ahmad-jajja_devabrteamabrlead-activity-7177855675555790848-Al_O?utm_source=share&utm_medium=member_desktop}{\underline{As a Dev Lead}}}, my focus is on the development side of our project ecofactor. I'm handling front-end, AI integration, and backend with my team. We, as Dev members, are working collaboratively on this project.}[{\href{https://www.linkedin.com/posts/ahmad-jajja_im-glad-i-could-contribute-to-the-project-activity-7172135900829605888-TSOY?utm_source=share&utm_medium=member_desktop}{\underline{See CEO Review}}}]
\resumeItem{EcoFactor currently consists of a team of 7 members: 4 from Pakistan, 2 from Brazil, and 1 from Latvia.[{\href{https://ecofactorsite.netlify.app/}{\underline{see team website}}}]}
\resumeItem{Utilizing these technologies to create EcoFactor: HTML, CSS, Bootstrap 5, JavaScript, React, Python, Flask, LLMs, Vectara, RAG.}
\resumeItemListEnd

\resumeSubheading
{Tech Trainer}{Dec 2022 -- Present}
{{\href{https://saylaniwelfareusa.com/en/services/education/technical-education/saylani-mass-it-training}{\underline{Saylani Mass IT Training Program}}}}{Faisalabad, PK}
\resumeItemListStart
\resumeItem{{\href{https://www.linkedin.com/posts/ahmad-jajja_learn-to-code-with-activity-7151895134744256512-Dmyf?utm_source=share&utm_medium=member_desktop}{\underline{Trained}}} 2000+ students to learn programming, DSA(LeetCode), web and mobile app development, and software engineering skills.}
\resumeItem{Programming Languages and Technologies : HTML, CSS (Bootstrap 5), JavaScript (ES6), TypeScript, DSA(LeetCode), React JS (Context API, Router, State Management), Next.js, NodeJS (ExpressJS, Authentication, API Endpoint Handling), NPM, MongoDB, Firebase, and React Native.}
\resumeItem{Hosting Platforms: Surge, gh-pages (GitHub Pages), Netlify, Vercel, and Firebase.}
\resumeItem{See students' reviews about how I impacted their coding(Development) journeys: ({\href{https://www.linkedin.com/posts/hassan-gulzar-256292267_javascript-problemsolvingskills-activity-7092472595249270784-PFDk?utm_source=share&utm_medium=member_desktop}{\underline{ Student1 }}}), ({\href{https://www.linkedin.com/posts/arhamansari12_nodejs-expressjs-mongodb-activity-7137844125382418432-SBrL?utm_source=share&utm_medium=member_desktop}{\underline{ Student2 }}}), ({\href{https://www.linkedin.com/feed/update/urn:li:activity:7171897869098962944/}{\underline{ Student3 }}}) and many more. }
\resumeItem{Students received training from me via these courses. See Github Repositories:}
\begin{itemize}
  \item {\href{https://github.com/Ahmadjajja/SMIT-Web-and-Mobile-Batch7}{\underline{Full Stack Development}}, \hspace{8pt} \href{https://github.com/Ahmadjajja/SMIT-WMA-6-A-E}{\underline{Frontend Web Development}}, \hspace{8pt} \href{https://github.com/Ahmadjajja/Mobile_Application_Development}{\underline{Frontend Mobile Development }}}
  \item {\href{https://github.com/Ahmadjajja/Backend_Development.git}{\underline{Backend Development}}, \hspace{12pt} \href{https://github.com/Ahmadjajja/Web_Designing_Crash_Course_A}{\underline{Web Designing Bootcamp B1}}, \hspace{6pt} \href{https://github.com/Ahmadjajja/Web_Designing_Crash_Course_B}{\underline{Web Designing Bootcamp B2}}}
  \item {\href{https://github.com/Ahmadjajja/AI-Chatbot}{\underline{AI Chatbot}}}
\end{itemize}
\resumeItemListEnd

\resumeSubheading
{MERN Stack Developer}{Sep 2022 - Mar 2023}
{ZW Tech}{Faisalabad, PK}
\resumeItemListStart
\resumeItem{Modified React JS front-end for UAE recruitment business website, resembling LinkedIn.}
\resumeItem{Developed Node.js-based GraphQL APIs, enhancing data management and integration
  for Dashboard.}
\resumeItem{Led the Desgning team and collaborated with product managers, business partners, and
  engineers to help define product requirements and roadmap .}
\resumeItemListEnd

\resumeSubheading
{MERN Stack Developer}{May 2022 - Aug 2022}
{Seeraht}{Faisalabad, PK}
\resumeItemListStart
\resumeItem{Developed and maintained MERN web apps at Seeraht, prioritizing quality, scalability, and
  efficiency.}
\resumeItem{Collaborated with cross-functional teams, implementing complex software features
  using modern development techniques.}
\resumeItem{Experience in integrating web applications with third-party APIs and services.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------6 - VOLUNTEER Experience-----------
\section{\textbf{Volunteer Experience}}
\resumeSubHeadingListStart
\resumeSubheading
{Section Leader Mentor}{Apr 2024 -- Jun 2024}
{{\href{https://codeinplace.stanford.edu/}{\underline{Stanford University: Code in Place}}}}{California, United States · Remote}
\resumeItemListStart
\resumeItem{{\href{https://www.linkedin.com/feed/update/urn:li:activity:7186385467846639620/}{\underline{Selected as a Section Leader}}} for Stanford's Code in Place to teach Python to international students in groups of 10-15.}
\resumeItem{Later, I was {\href{https://www.linkedin.com/posts/ahmad-jajja_stanfordabrcodeabrinabrplaceabrlearnings-activity-7195142429073633281-zNhV?utm_source=share&utm_medium=member_desktop}{\underline{promoted to Section Leader Mentor}}} for one-on-one student support and {\href{https://www.linkedin.com/feed/update/urn:li:activity:7204425552311541760/}{\underline{taught 56 TeachNow}}} sessions.}
\resumeItem{ I helped 100+ international folks worldwide, including countries like the USA, Canada, Russia, the UK, India, Bangladesh, Brazil, Germany, and others.}
\resumeItemListEnd
\resumeSubheading
{Trainer and Moderator}{Feb 2023 -- Present}
{{\href{https://www.linkedin.com/company/icode-guru/mycompany/}{\underline{iCodeGuru}}}}{Santa Clara, California · Remote}
\resumeItemListStart
\resumeItem{{\href{https://github.com/Ahmadjajja/LeetCode_Volunteer_Teaching}{\underline{Offered}}} volunteer teaching in Python and DSA at iCodeGuru, emphasizing LeetCode.}
\resumeItem{{\href{https://www.linkedin.com/feed/update/urn:li:activity:7169346246216671232/}{\underline{Taught}}} course on the Duolingo English Proficiency Test.}
\resumeItem{{\href{https://github.com/Ahmadjajja/Machine-Learning_and_its-privacy-implications}{\underline{Delivering}}} "Machine Learning from Scratch \& Its Privacy Implications" training to underprivileged students.}
\resumeItem{Conducting weekly workshops especially to help underprivileged students to learn freely.{\href{https://github.com/Ahmadjajja/LeetCode_Volunteer_Teaching}{\underline{[See here]}}}}
\resumeItem{See students' reviews about how I impacted their coding(DSA + LeetCode) journeys : ({\href{https://www.linkedin.com/posts/sikander-nawaz_dsa-dsa-leetcode-activity-7170805639886106624-Kxka?utm_source=share&utm_medium=member_desktop}{\underline{ Student1 }}}), ({\href{https://www.linkedin.com/posts/syedshahzilimran_mastering-trees-unlocking-the-key-of-dsa-activity-7174974045019398144-DN_C?utm_source=share&utm_medium=member_desktop}{\underline{ Student2 }}}), ({\href{https://www.linkedin.com/feed/update/urn:li:activity:7173635314391920640/}{\underline{ Student3 }}}) and many more. }
\resumeItemListEnd
\resumeSubHeadingListEnd
%



%-----------7 - Hackathons & Competitions-----------
\section{\textbf{Hackathons and Competitions}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{{Harvard's CS50x Puzzle Day 2024}} $|$ [{\href{https://www.linkedin.com/feed/update/urn:li:activity:7184212040717131778/}{\underline{LinkedIn link}}}]}{}
\resumeItemListStart
\resumeItem{Led a 5-member team to 1st place at Harvard's CS50x Puzzle Day 2024.}
\resumeItem{Solved 9 complex puzzles using deep logical thinking and teamwork.}
\resumeItem{Collaborated with international members from Greece, Nigeria, and Pakistan.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{{Neue View}} $|$ \emph{HTML, CSS, Bootstrap5, Javascript, React, Open AI Model GPT-3.5 Turbo, OCR, Trulens, Pinecone, python, Flask} $|$ [{\href{https://github.com/Ahmadjajja/neue-view}{\underline{Github link}}}]} {}
\resumeItemListStart
\resumeItem{AI-Powered Web-Based OCR Solution for Digitizing and Analyzing Handwritten Information.[{\href{https://www.linkedin.com/feed/update/urn:li:activity:7167991035099385856/}{\underline{LinkedIn link}}}]}
\resumeItem{The Neue View Project involved a team of six individuals from United States and Pakistan.The [{\href{https://lablab.ai/event/gpt-4-powered-app-creation-hackathon/neue-view/neue-view}{\underline{lablab.ai submission link}}}]}
\resumeItem{Managed the whole development project.}
\resumeItem{Senior dev: frontend Design, backend design(rest api's creation using python and flask), backend and AI integration.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{{Full Stack Real Estate Mobile App}} $|$ \emph{Javascript, ReactNative, Redux, ContextAPI, NodeJS,
    ExpressJS, MongoDB} $|$ [{\href{https://github.com/Ahmadjajja/Social_Real_Estate_System_Mobile_App_Frontend}{\underline{Github link}}}]}{}
\resumeItemListStart
\resumeItem{Participated in a national hackathon at Saylani Mass IT Training Program in August 2022.}
\resumeItem{Project with authentication, dashboard, property
  management, searching, browsing and call-to-action feature for property
  tansactions, powered by REST APIs using Node JS.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{{Coding Competitions}}}{}
\resumeItemListStart
\resumeItem{Qualified for : “{\href{https://www.linkedin.com/feed/update/urn:li:activity:7053083509342576640/}{\underline{Google Code Jam 2023}}} and {\href{https://github.com/Ahmadjajja/MetaHackerCup2023}{\underline{Meta Hacker Cup 2023}}}”.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%

%-----------8 - PERSONAL PROJECTS-----------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{{Plant Disease Detection System}} $|$ \emph{Python (Flask, TensorFlow, Keras, OpenCV, Pillow, NumPy, Matplotlib, Seaborn)} $|$ [{\href{https://github.com/Ahmadjajja/E_Commerce_Mobile_App_Frontend}{\underline{Github link}}}]}{}
\resumeItemListStart
\resumeItem{Developed and deployed a Flask web application to detect plant diseases from leaf images using a trained convolutional neural network (CNN).}
\resumeItem{Preprocessed and augmented a comprehensive dataset of plant leaf images, categorized into healthy, powdery mildew, and rust classes to enhance model accuracy.}
\resumeItem{Designed and trained the CNN model using TensorFlow and Keras, achieving high accuracy in classifying plant diseases.}
\resumeItem{Implemented image processing techniques with OpenCV and Pillow to handle image uploads and preparation for prediction in the web application.}
\resumeItemListEnd
{\textbf{{Full Stack Bank WEB APP}} $|$ \emph{HTML, CSS, Bootstrap5, Javascript, React, Context API, Firebase, Firestore} $|$ [{\href{https://github.com/Ahmadjajja/React_Bank}{\underline{Github link}}}]}{}
\resumeItemListStart
\resumeItem{Bank-App is a web application allowing users to manage accounts, perform
  transactions, and view transaction history conveniently.[{\href{https://jajja-bank-app.web.app/}{\underline{Live link}}}]}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{{Full Stack E-Commerce Mobile App}} $|$ \emph{Javascript, ReactNative, Redux, ContextAPI, NodeJS,
    ExpressJS, MongoDB} $|$ [{\href{https://github.com/Ahmadjajja/E_Commerce_Mobile_App_Frontend}{\underline{Github link}}}]}{}
\resumeItemListStart
\resumeItem{E-commerce mobile app with user registration, product catalog, cart, wishlist,
  checkout, payment, order tracking, and admin dashboard.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------9 - REFERENCES-----------
\section{\textbf{References}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{{Dr. Zafar Shahid}} $|$ \emph{Technical Lead/ Staff Engineer @Meta} $|$ {\href{https://www.linkedin.com/in/zafarshahid/}{\underline{LinkedIn}}}}{}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape Email:} zafar.shahid@acm.org}
\resumeItem{\textcolor{blue}{\itshape Phone:} +1 512 239 8008}
\resumeItem{\textcolor{blue}{\itshape Location:} Santa Clara, California, United States}
\resumeItemListEnd
{\textbf{{Dr. Rizwan Ghaffar}} $|$ \emph{Principal Engineer @Broadcom Inc.} $|$ {\href{https://www.linkedin.com/in/rizwan-ghaffar-8283231a/}{\underline{LinkedIn}}}}{}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape Email:} rizwanghaffar24@gmail.com}
\resumeItem{\textcolor{blue}{\itshape Phone:} +1 858 216 5405}
\resumeItem{\textcolor{blue}{\itshape Location:} San Jose, California, United States}
\resumeItemListEnd
{\textbf{{Bruno Cesar}} $|$ \emph{Senior UI/UX Designer, Creative ChatGPT Researcher, Prompt Engineer and Teacher.} $|$ {\href{https://www.linkedin.com/in/brunoalecrim/}{\underline{LinkedIn}}}}{}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape Email:} alecrim.bruno@gmail.com}
\resumeItem{\textcolor{blue}{\itshape Phone:} +55 21 99997 3045}
\resumeItem{\textcolor{blue}{\itshape Location:} Rio de Janeiro, Brazil}
\resumeItemListEnd
{\textbf{{Pariphat SInma}} $|$ \emph{Product Designer, Design Innovator Bridging Emerging Technologies and Brands Globally} $|$ {\href{https://www.linkedin.com/in/pariphat-sinma/}{\underline{LinkedIn}}}}{}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape Email:} pariphat.s@gmail.com}
\resumeItem{\textcolor{blue}{\itshape Phone:} +1 224 382 3483}
\resumeItem{\textcolor{blue}{\itshape Location:} Chicago, Illinois, United States}
\resumeItemListEnd
{\textbf{{Wajeeha Azmat}} $|$ \emph{Lecturer at University of Agriculture, Faisalabad} $|$ {\href{https://www.linkedin.com/in/wajeehaazmat/}{\underline{LinkedIn}}}}{}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape Email:} wajeeha.azmat@uaf.edu.pk}
\resumeItem{\textcolor{blue}{\itshape Phone:} +92 303 402 9300}
\resumeItem{\textcolor{blue}{\itshape Location:} Faisalabad, Pakistan}
\resumeItemListEnd
\resumeSubHeadingListEnd

%

%-------------------------------------------
\end{document}
